\documentclass{article}
\usepackage{neurips_2026}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\usepackage[T1]{fontenc}
\frenchspacing  % DO NOT CHANGE THIS
\usepackage{algorithm}
\usepackage{algorithmic}
\pagestyle{plain}
\usepackage{threeparttable}
\input{math_commands.tex}
\usepackage{lineno}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{cases}
\captionsetup{compatibility=false}
\usepackage{epstopdf}
\usepackage{placeins}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{calc}
\usepackage{array}
%\usepackage{todonotes}
%\newcommand\eca[1]{\textcolor{red}{#1}}
% allow to type " and get latex to handle it
\usepackage[autostyle=false, style=english]{csquotes}
\MakeOuterQuote{"}

%\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usetikzlibrary{positioning, arrows.meta,calc}
\usepackage{newfloat}
\usepackage{listings}
\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
\lstset{%
	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
	aboveskip=0pt,belowskip=0pt,%
	showstringspaces=false,tabsize=2,breaklines=true}
\floatstyle{ruled}
\newfloat{listing}{tb}{lst}{}
\floatname{listing}{Listing}
\usepackage{amsthm}
\newtheorem{proposition}{Proposition}
%\newtheorem{definition}{Definition}
\newcommand{\vW}{\boldsymbol{W}}
\newcommand{\val}{{\textrm{value}}}
\newcommand{\Val}{{\textrm{value}}}
\newcommand{\MILP}{{\textrm{MILP}}}
\newcommand{\LP}{{\textrm{LP}}}
\newcommand{\Improve}{\mathrm{Improve}}
\newcommand{\Utility}{\mathrm{SAS}}
\newcommand{\Sol}{\mathrm{Sol}}
\newcommand{\sol}{\mathrm{sol}}
\newcommand{\UB}{\mathrm{UB}}
\newcommand{\LB}{\mathrm{LB}}
\newcommand{\ub}{\mathrm{ub}}
\newcommand{\lb}{\mathrm{lb}}
\newcommand{\B}{\mathrm{B}}
\usepackage{amsmath, amssymb, amsfonts}
\newcommand{\ReLU}{\mathrm{ReLU}}
\newcommand{\CMP}{{\textrm{CMP}}\ }
\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
\newcommand{\toolname}{Hybrid MILP}
\usepackage{bibentry}




\title{Formatting Instructions For NeurIPS 2026}

\author{%
	David S.~Hippocampus\thanks{Use footnote for providing further information
		about author (webpage, alternative address)---\emph{not} for acknowledging
		funding agencies.} \\
	Department of Computer Science\\
	Cranberry-Lemon University\\
	Pittsburgh, PA 15213 \\
	\texttt{hippo@cs.cranberry-lemon.edu} \\
	% examples of more authors
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
	% \AND
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
}




\begin{document}
	
	
	\maketitle
	
	
	\begin{abstract}
		The abstract paragraph should be indented \nicefrac{1}{2}~inch (3~picas) on both the left- and right-hand margins. Use 10~point type, with a vertical spacing (leading) of 11~points. The word \textbf{Abstract} must be centered, bold, and in point size 12. Two line spaces precede the abstract. The abstract must be limited to one paragraph.
	\end{abstract}
	
	
	\section{Introduction}
	
	\input{introduction}
	
	\input{related}
	
	\input{notation}
	
	\input{global}
	
	\input{PCA}
	
	\input{experiments}
	
	\input{pipe}
	
	
	%\newpage
	%\vspace{-0.5cm}
	
	
	
	\section{Conclusion}
	
	In this paper, we introduced a novel {\em Diff} MILP model for {\em global} verification questions, which is more accurate than the classical MILP model,
	even when using optimizations, namely the ITNE model of \citet{lipshitz,ITNE}
	and VHAGaR \citet{vhagar}; see Table \ref{table.classical}. 
	We also explained how to support $L_1$-perturbations efficiently on top of classical $L_\infty$-perturbations.
	Further, using simpler models, namely with the {\em 2b+1}
	or the {\em 1b} models, abstracting away some features of the {\em Diff} model,
	even better bounds can be reached for the complex questions of global robustness with $L_1$ bounds (Tables 3, 5). To further lower the bounds by $3-20$ times, we resort to PCA, concentrating the accuracy around the datasets, potentially being inaccurate for OOD inputs, over which the DNN is mostly inaccurate anyway, without sacrificing DNN accuracy over the dataset. 
	This results into, to the best of our knowledge, the first {\em real-time} robustness certification reported for a DNN, with $\geq 70\%$ of robustness for an $L_1$-perturbation of $\geq 1$ for different datasets. Still, global verification is only at its beginning, and combining different methods is necessary to scale to more complex DNNs.
	
	\newpage
	
	\bibliographystyle{plainnat}
	\bibliography{references}
	
	\newpage
	
\appendix

	\input{appendix}
\end{document}
