\subsection{Related Work on Global Robustness}

While \citet{diff} does not tackle global robustness per se, it is one of the first works to consider {\em differential} verification, introducing the {\em diff} variables that are used here and also in \citet{ITNE}. The paper \citet{diff} did not consider MILP encoding.
%
Some works \citet{Leino,Zhang22a,Sun22,Chen21,REGLO} focus on training a network to be, rather than proving the DNN is, globally robust.
Other works \citet{Bastani16,Ruan19,Gopinath18} estimate global robustness bounds, but without hard verification certificates, e.g., using probabilistic guarantees \citet{Levy23,Mangal19}.

More related, several works  \citet{Marabou,lipshitz,ITNE,GROCET} consider certifying {\em restricted} Lipschitz bound, to understand how the output can change given an input perturbation. However, they do not consider whether the classification changes. 
%
Closest to our work is VHAGaR \citet{vhagar}, which computes 
bounds $\bar{\alpha}^\varepsilon_{i,j}$ similar to our bounds 
$\bar{\beta}^\varepsilon_{i,j}$, but limited to $L_\infty$-perturbations and variants. Crucially, VHAGaR bounds are not small enough for real-time robustness verification, whereas our bounds are. One reason is {\em Diff} MILP is more accurate in practice, the other is that LAE-DNNis intrinsically more robust.
{\color{red}Paragraph on (L)AE-DNN}




Technically, none of the MILP-based works \citet{vhagar,lipshitz,ITNE} consider $L_1$-perturbations. Further, they use the classical MILP encoding from \citet{MILP}, and not our novel {\em Diff} model, nor even the "1b" model. Note that \citet{ITNE} considers the {\em diff variables} $y,\hat{y}$, adding explicitly one {\em linear} constraint $\frac{y_i-\gamma_i}{2} \leq \hat{y}_i \leq \frac{y_i+\gamma_i}{2}$ implied by each of our three MILP models {\em Diff}, "2b+1" and "1b" models; Eq. (3) in \citet{ITNE} corresponding essentially to it. \citet{vhagar} does things differently, adding per neuron constraints (depending on the perturbation) between the (binary) variables to simplify the MILP problem, which is well-adapted to occlusion and patches but less to $L_1$-perturbations. 
%(and to some extent to $L_\infty$-perturbations). 

